\section{Exercises}
\subsection{1.2: Mathematical Statements}
    \begin{enumerate}
        \item 
            \begin{enumerate}
                \item Not a statement
                \item Atomic statement
                \item Molecular statement
            \end{enumerate}
        \item
            \begin{enumerate}
                \item Not a statement
                \item Atomic statement
                \item Molecular statement with conditional.
                \item Molecular statement with biconditional.
                \item Molecular statement with disjunction.
                \item Molecular statement with negation.
            \end{enumerate}
        \item
            \begin{enumerate}
                \item $P \wedge Q$
                \item $P \rightarrow \neg Q$
                \item "Jack passed math or Jill passed math."
                \item "If Jack did not pass math or Jill did not pass math, then Jill passed math."
                \item 
                    \begin{enumerate}
                        \item Only that Jill passed math.
                        \item Jack did not pass math.
                    \end{enumerate}
            \end{enumerate}
        \item
            \begin{enumerate}
                \item Not enough info.
                \item True
                \item True
                \item True
                \item Not enough info.
                \item False
                \item True
            \end{enumerate}
        \item
            \begin{enumerate}
                \item False
                \item Not enough info.
                \item True
                \item Not enough info.
                \item True
            \end{enumerate}
        \item 
            \begin{enumerate}
                \item False
                \item True
                \item False
                \item True
            \end{enumerate}
        \item b is the contrapositive, and c is the converse. 
        \item 
            \begin{enumerate}
                \item If Oscar drinks milk, then he eats Chinese food.
                \item If Oscar does not drink milk, then he does not eat Chinese food.
                \item If the contrapositive was false, then the original statement would be false. They are equivalent.
                \item No. Q is not a part of the if statement, it is only the result.
                \item Yes. You know that since he does not drink milk, he will not eat Chinese food. This is because of the contrapositive.
            \end{enumerate}
        \item 
            \begin{enumerate}
                \item Converse
                \item Original
                \item Converse
                \item Original
                \item Original
                \item Converse
                \item Converse
                \item Original
            \end{enumerate}
        \item
            \begin{enumerate}
                \item If you lose weight, you must exercise.
                \item If all you do is exercise, you will lose weight.
                \item If you are American, you are patriotic.
                \item If you are patriotic, you are American.
                \item If a number is rational, then it is real.
                \item If a number is not even, it is prime.
                \item If the Broncos don't win the Super Bowl, they won't play in the Super Bowl.
            \end{enumerate}
    \end{enumerate}